Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-05 inc/model_results/shapes/shapes.tex
ok I have decided to go with w_{\smallT} rather than just assume the _{\smallT}

The initial `space-time' eccentricity (defined in \ref{eq:define_xi}),
\begin{equation}
  \xi ( 0 ) = \sqrt{ \frac{ \sigma_{z}(0) }{ \sigma_{\smallT}(0) } } = \frac{ w_z(0) }{ w(0) } = \frac{ v_{\smallzero} \tau(0) }{ w(0) } \,\text{,}
\end{equation}
of the photo-generated electron pulse plays a major role in the bunch propagation dynamics, particularly when space-charge effects dominate.
\ref{fig:compare_shape} illustrates the typical dynamics of initially spherical ($ \xi(0) = 1 $), oblate or `disk-like' ($ \xi(0) < 1 $), and prolate or `cigar-like' ($ \xi(0) > 1 $) pulses.
%TODO rewrite using w?
This simulation uses the idealized pulse conditions described above, where the initial bunch dimensions are given by the ellipticities $ \xi(0) = \{ 1/3 , 1 , 3 \} $ and in each case the product of the initial HW1/eM bunch widths $w^2 w_z = $ 1mm$^3$.
Pulses used in \ref{fig:compare_shape}\subref{fig:compare_shape_N1} have just one electron per pulse (i.e. $ N = 10^{0} $), while \ref{fig:compare_shape}\subref{fig:compare_shape_N1e6} have a much higher $ N = 10^{6} $ electrons in the bunch.
Since the initial pulse volume is consistent between all runs, initial peak pulse charge density is six orders of magnitude greater in \ref{fig:compare_shape}\subref{fig:compare_shape_N1e6} than in \ref{fig:compare_shape}\subref{fig:compare_shape_N1}.
The pulse velocity is $ v_{\smallzero} \approx c/3 $, which is equivalent to a DC photogun with $V_{DC} = 30\text{kV} $.

>>>>

The initial `space-time' eccentricity (defined in \ref{eq:define_xi}),
\begin{equation}
  \xi ( 0 ) = \sqrt{ \frac{ \sigma_{z}(0) }{ \sigma_{\smallT}(0) } } = \frac{ w_z(0) }{ w_{\smallT}(0) } = \frac{ v_{\smallzero} \tau(0) }{ w_{\smallT}(0) } \,\text{,}
\end{equation}
of the photo-generated electron pulse plays a major role in the bunch propagation dynamics, particularly when space-charge effects dominate.
\ref{fig:compare_shape} illustrates the typical dynamics of initially spherical ($ \xi(0) = 1 $), oblate or `disk-like' ($ \xi(0) < 1 $), and prolate or `cigar-like' ($ \xi(0) > 1 $) pulses.
%TODO rewrite using w?
This simulation uses the idealized pulse conditions described above, where the initial bunch dimensions are given by the ellipticities $ \xi(0) = \{ 1/3 , 1 , 3 \} $ and in each case the product of the initial HW1/eM bunch widths $w_{\smallT}^2 w_z = $ 1mm$^3$.
Pulses used in \ref{fig:compare_shape}\subref{fig:compare_shape_N1} have just one electron per pulse (i.e. $ N = 10^{0} $), while \ref{fig:compare_shape}\subref{fig:compare_shape_N1e6} have a much higher $ N = 10^{6} $ electrons in the bunch.
Since the initial pulse volume is consistent between all runs, initial peak pulse charge density is six orders of magnitude greater in \ref{fig:compare_shape}\subref{fig:compare_shape_N1e6} than in \ref{fig:compare_shape}\subref{fig:compare_shape_N1}.
The pulse velocity is $ v_{\smallzero} \approx c/3 $, which is equivalent to a DC photogun with $V_{DC} = 30\text{kV} $.
